---
title: "Assignment V: GitHub and the ticketmaster.com API" 
subtitle: "Data Science Project Management | Winter Term 2020/21"
author: "Dantong QU  5400692" 
output: html_document
---

```{r echo=TRUE, message=FALSE}
rm(list = ls())
setwd("~/Desktop/DS400 Data Science Project Management /Assignment 5/Assignment_5")

if (!require("jsonlite")) install.packages("jsonlite")
if (!require("httr")) install.packages("httr")
if (!require("rlist")) install.packages("rlist")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("naniar")) install.packages("naniar")
if (!require("devtools")) install.packages("devtools")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("gridExtra")) install.packages("gridExtra")
if (!require("dplyr")) install.packages("dplyr")
if (!require("directlabels")) install.packages("directlabels")
if (!require("ggrepel")) install.packages("ggrepel")

library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)
library(devtools)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(directlabels)
library(ggrepel)
```

### 1. Setting up a new GitHub repository
https://github.com/Dantong-Qu/Assignment_5.git

### 2. Getting to know the API

Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at rate limits.

All API keys are issued with a default quota of 5000 API calls per day and rate limitation of 5 requests per second. 
```{r echo=TRUE, message=FALSE}
source("API_key.R")
```

### 3. Interacting with the API - the basics

```{r echo=TRUE, message=FALSE}
# Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). 
get_tm <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
              query = list(apikey = tm_key,
                           locale = "*",
                           countryCode = "DE"))

# Extract the content from the response object and inspect the resulting list. 
content <- fromJSON(content(get_tm, as = "text", encoding = "UTF-8"))
venues <- content[["_embedded"]][["venues"]]
glimpse(venues)
```
Describe what you can see.

After the first GET request, the response object contains the list element that we want to extract (the comtent), but in row format, it is not easily understandable, so we use the content() function to extract and understand the data, and fromJSON() function help us to consistent and robust converting between JSON and R formats. So we conbine those two function together. In the content data, we can see there are three lists, the information we need in the next task are in the content$_embedded$venues, and the other lists are "_links" and "page".

```{r echo=TRUE, message=FALSE}
venue_data <- data.frame(venues$name, 
                         venues$city$name, 
                         venues$postalCode, 
                         venues$address$line1, 
                         venues$url, 
                         venues$location$longitude, 
                         venues$location$latitude)

names(venue_data)[1] <- "name"
names(venue_data)[2] <- "city"
names(venue_data)[3] <- "postalCode"
names(venue_data)[4] <- "address"
names(venue_data)[5] <- "url"
names(venue_data)[6] <- "longitude"
names(venue_data)[7] <- "latitude"

glimpse(venue_data)
```

### 4. Interacting with the API - advanced
From exercise 3 we did not return all event locations in Germany, because there are 612 pages and we only get the information from the first page, so here we use a for loop the return all the informations.
```{r echo=TRUE, message=FALSE}
pages <- as.numeric(content$page$totalPages) - 1
n <- as.numeric(content$page$totalElements)
remainder <- n-20*pages

venue_data4 <-
  data.frame(name = character(n),
             city = character(n),
             postalCode = character(n),
             address = character(n),
             url = character(n),
             longitude = character(n),
             latitude = character(n),
             stringsAsFactors = FALSE)

# Actually the first page is from page 0, so we loop from 0 to the last full page (pages-1)
for (i in 0:pages-1) {
  get_venue <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                                    query = list(apikey = tm_key,
                                                 locale = "*",
                                                 countryCode = "DE",
                                                 page = i))
  
  venues4 <- fromJSON(content(get_venue, as = "text", encoding = "UTF-8"))[["_embedded"]][["venues"]]

  ifelse(is.null(venues4$name),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"name"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"name"] <- venues4$name)
  ifelse(is.null(venues4$city$name),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"city"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"city"] <- venues4$city$name)
  ifelse(is.null(venues4$postalCode),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"postalCode"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"postalCode"] <- venues4$postalCode)
  ifelse(is.null(venues4$address$line1),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"address"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"address"] <- venues4$address$line1)
  ifelse(is.null(venues4$url),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"url"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"url"] <- venues4$url)
  ifelse(is.null(venues4$location$longitude),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"longitude"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"longitude"] <- venues4$location$longitude)
  ifelse(is.null(venues4$location$latitude),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"latitude"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"latitude"] <- venues4$location$latitude)
  Sys.sleep(0.2)
  }

# add the last page
i <- i+1
get_venue <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                 query = list(apikey = tm_key,
                              locale = "*",
                              countryCode = "DE",
                              page = i))
venues4 <- fromJSON(content(get_venue, as = "text", encoding = "UTF-8"))[["_embedded"]][["venues"]]

ifelse(is.null(venues4$name),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"name"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"name"] <- venues4$name)
ifelse(is.null(venues4$city$name),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"city"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"city"] <- venues4$city$name)
ifelse(is.null(venues4$postalCode),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"postalCode"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"postalCode"] <- venues4$postalCode)
ifelse(is.null(venues4$address$line1),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"address"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"address"] <- venues4$address$line1)
ifelse(is.null(venues4$url),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"url"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"url"] <- venues4$url)
ifelse(is.null(venues4$location$longitude),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"longitude"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"longitude"] <- venues4$location$longitude)
ifelse(is.null(venues4$location$latitude),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"latitude"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"latitude"] <- venues4$location$latitude)
glimpse(venue_data4)
```

### 5. Visualizing the extracted data
```{r echo=TRUE, message=FALSE}
# Set coordinate values to NA where the value of longitude is outside the range (5.866944, 15.043611) or where the value of latitude is outside the range (47.271679, 55.0846) 

range <- data.frame(longitude_range = c(5.866944, 15.043611), latitude_range = c(47.271679, 55.0846))

venue_data4$longitude <- ifelse((as.numeric(venue_data4$longitude) > range[1,1]), venue_data4$longitude, NA)
venue_data4$longitude <- ifelse((as.numeric(venue_data4$longitude) < range[2,1]), venue_data4$longitude, NA)
venue_data4$latitude <- ifelse((as.numeric(venue_data4$latitude) > range[1,2]), venue_data4$latitude, NA)
venue_data4$latitude <- ifelse((as.numeric(venue_data4$latitude) < range[2,2]), venue_data4$latitude, NA)

# Unique the cities
ggplot(data = venue_data4, aes(x = as.numeric(longitude), y = as.numeric(latitude))) + 
  geom_polygon(aes(x = long, y = lat, group = group), 
               data = map_data("world", region = "Germany"),
               fill = "grey90",
               color = "black") +
  geom_point(color = "#1E88E5", alpha = 0.7) +
  # geom_text_repel(aes(x = as.numeric(longitude), y = as.numeric(latitude), label = city)) +
  theme_void() + 
  coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") + 
  theme(title = element_text(size=8, face='bold'), plot.caption = element_text(face = "italic"))
```
### 6. Event locations in other countries
Here we choose county : Switzerland.
```{r echo=TRUE, message=FALSE}
get_tm <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
              query = list(apikey = tm_key,
                           locale = "*",
                           countryCode = "CH"))
content <- fromJSON(content(get_tm, as = "text", encoding = "UTF-8"))
venues <- content[["_embedded"]][["venues"]]
glimpse(venues)

venue_data <- data.frame(venues$name, 
                         venues$city$name, 
                         venues$postalCode, 
                         venues$address$line1, 
                         venues$url, 
                         venues$location$longitude, 
                         venues$location$latitude)

names(venue_data)[1] <- "name"
names(venue_data)[2] <- "city"
names(venue_data)[3] <- "postalCode"
names(venue_data)[4] <- "address"
names(venue_data)[5] <- "url"
names(venue_data)[6] <- "longitude"
names(venue_data)[7] <- "latitude"

glimpse(venue_data)

pages <- as.numeric(content$page$totalPages) - 1
n <- as.numeric(content$page$totalElements)
remainder <- n-20*pages

venue_data4 <-
  data.frame(name = character(n),
             city = character(n),
             postalCode = character(n),
             address = character(n),
             url = character(n),
             longitude = character(n),
             latitude = character(n),
             stringsAsFactors = FALSE)

for (i in 0:pages-1) {
  get_venue <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                                    query = list(apikey = tm_key,
                                                 locale = "*",
                                                 countryCode = "CH",
                                                 page = i))
  
  venues4 <- fromJSON(content(get_venue, as = "text", encoding = "UTF-8"))[["_embedded"]][["venues"]]

  ifelse(is.null(venues4$name),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"name"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"name"] <- venues4$name)
  ifelse(is.null(venues4$city$name),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"city"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"city"] <- venues4$city$name)
  ifelse(is.null(venues4$postalCode),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"postalCode"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"postalCode"] <- venues4$postalCode)
  ifelse(is.null(venues4$address$line1),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"address"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"address"] <- venues4$address$line1)
  ifelse(is.null(venues4$url),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"url"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"url"] <- venues4$url)
  ifelse(is.null(venues4$location$longitude),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"longitude"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"longitude"] <- venues4$location$longitude)
  ifelse(is.null(venues4$location$latitude),
         venue_data4[(i * 20 + 1):((i + 1) * 20),"latitude"] <- NA,
         venue_data4[(i * 20 + 1):((i + 1) * 20),"latitude"] <- venues4$location$latitude)
  Sys.sleep(0.2)
  }

i <- i+1
get_venue <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                 query = list(apikey = tm_key,
                              locale = "*",
                              countryCode = "CH",
                              page = i))
venues4 <- fromJSON(content(get_venue, as = "text", encoding = "UTF-8"))[["_embedded"]][["venues"]]

ifelse(is.null(venues4$name),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"name"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"name"] <- venues4$name)
ifelse(is.null(venues4$city$name),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"city"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"city"] <- venues4$city$name)
ifelse(is.null(venues4$postalCode),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"postalCode"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"postalCode"] <- venues4$postalCode)
ifelse(is.null(venues4$address$line1),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"address"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"address"] <- venues4$address$line1)
ifelse(is.null(venues4$url),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"url"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"url"] <- venues4$url)
ifelse(is.null(venues4$location$longitude),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"longitude"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"longitude"] <- venues4$location$longitude)
ifelse(is.null(venues4$location$latitude),
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"latitude"] <- NA,
       venue_data4[(i * 20 + 1):(i * 20 + remainder),"latitude"] <- venues4$location$latitude)
glimpse(venue_data4)

range <- data.frame(longitude_range = c(5.57, 10.29), latitude_range = c(45.49, 47.48))

venue_data4$longitude <- ifelse((as.numeric(venue_data4$longitude) > range[1,1]), venue_data4$longitude, NA)
venue_data4$longitude <- ifelse((as.numeric(venue_data4$longitude) < range[2,1]), venue_data4$longitude, NA)
venue_data4$latitude <- ifelse((as.numeric(venue_data4$latitude) > range[1,2]), venue_data4$latitude, NA)
venue_data4$latitude <- ifelse((as.numeric(venue_data4$latitude) < range[2,2]), venue_data4$latitude, NA)

ggplot(data = venue_data4, aes(x = as.numeric(longitude), y = as.numeric(latitude))) + 
  geom_polygon(aes(x = long, y = lat, group = group), 
               data = map_data("world", region = "Switzerland"),
               fill = "grey90",
               color = "black") +
  geom_point(color = "#1E88E5", alpha = 0.7) +
  geom_text_repel(aes(x = as.numeric(longitude), y = as.numeric(latitude), label = city)) +
  theme_void() + 
  coord_quickmap() +
  labs(title = "Event locations across Switzerland", caption = "Source: ticketmaster.com") + 
  theme(title = element_text(size=8, face='bold'), plot.caption = element_text(face = "italic"))

```







